Persistence in functional topology: q-tameness, local-connectivity and a correction to a theorem of Morse

### 2021-04-01 counterexample.tex
Change counterexample: statement using conditions on H-theory

\begin{figure}[t]
	\centering
	\begin{tikzpicture}[scale=88]
	\draw[thick] (-.1,0) rectangle (.1,.05);
	\clip (-.1,0) rectangle (.1,.05); % remove for all circles
	\foreach \i in {1,...,100}{
		\draw[line width=0.1/\i mm] (0, 1/\i^2) circle (1/\i^2);
	}
	\end{tikzpicture}
	\caption{A closeup of the Hawaiian hearing $\mathbb{H}^1$.}
	\label{fig:earrings}
\end{figure}

In this section we show that a sublevel filtration can be $\HLC$ and not q-tame for most homology theories of interest.

@@

\begin{thm} \label{thm:counterexample}
	Let $\H$ be a homology theory such that its value on a point is finitely generated for every degree and on $\HE$ is not finitely generated for some degree. Then, the function $f \colon \HE \to \R$ whose value at the origin is $0$ and is $1$ everywhere else defines a $\HLC$ Morse filtration that is not q-tame.
\end{thm}

\begin{proof}
	The space $\HE$ is Hausdorff and locally compact since $R^{d+1}$ is.
	To verify that $(\HE,f)$ is a Morse filtration we notice that all level sets are either the empty set, the singleton containing the origin, or $\HE$ itself, all compact spaces.
	Let us now verify that $\HE$ is $\HLC$.
	Let $\epsilon > 0$ and $x \in \HE$.
	If $x$ is the origin, we choose $\delta$ between $0$ and the minimum of $\epsilon$ and $1$.
	Then $\HE_{\leq f(x) + \delta} = \HE_{\leq \delta} = \{x\}$, so the desired condition follows from the first assumption on the homology theory.
	For $x$ not the origin, there is a unique $d$-sphere that contains it.
	Clearly, we may choose $\delta > 0$ so small that $D_\delta(x) = \{y \in \R^{d+1} \mid \Vert x - y \Vert < \delta\} \cap \HE$ is contained in this sphere, so $D_\delta(x)$ is homotopy equivalent to a $x$ and the condition again follows trivially.
	What remains to be shown is that $\HE_{\leq \bullet}$ is not q-tame.
	Since $\HE_{\leq t}$ is constant with value $\HE$ for $t \geq 1$, the second assumption on the homology theory finishes the proof.
\end{proof}

>>>>

\begin{figure}[t]
	\centering
	\begin{tikzpicture}[scale=88]
	\draw[thick] (-.1,0) rectangle (.1,.05);
	\clip (-.1,0) rectangle (.1,.05); % remove for all circles
	\foreach \i in {1,...,100}{
		\draw[line width=0.1/\i mm] (0, 1/\i^2) circle (1/\i^2);
	}
	\end{tikzpicture}
	\caption{TBW}
	\label{fig:earrings}
\end{figure}

In this section we show that a sublevel filtration can be $\HLC$ and not q-tame.

@@

\begin{thm} \label{thm:counterexample}
	Let $\H$ be a homology theory such that its value at a point is finitely generated for every degree and at $\HE$ is not finitely generated in some degree. Then, the function $f \colon \HE \to \R$ whose value at the origin is $0$ and is $1$ everywhere else defines a $\HLC$ Morse filtration that is not q-tame.
\end{thm}

\begin{proof}
	The space $\HE$ is Hausdorff and locally compact since $R^{d+1}$ is.
	To verify that $(\HE,f)$ is Morse we notice that all level sets are either the empty set, the singleton containing the origin, or $\HE$ itself, all compact spaces.
	Let us now verify that $\HE$ is $\HLC$.
	Let $\epsilon > 0$ and $x \in \HE$.
	If $x$ is the origin, we choose $\delta$ between $0$ and the minimum of $\epsilon$ and $1$.
	Then $\HE_{\leq f(x) + \delta} = \HE_{\leq \delta} = \{x\}$, so the desired condition follows from the first assumption on the homology theory.
	For $x$ not the origin, there is a unique $d$-sphere that contains it.
	Clearly, we may choose $\delta > 0$ so small that $D_\delta(x) = \{y \in \R^{d+1} \mid \Vert x - y \Vert < \delta\} \cap \HE$ is contained in this sphere, so $D_\delta(x)$ is homotopy equivalent to a $x$ and the condition again follows trivially.
	What remains to be shown is that $\HE_{\leq \bullet}$ is not q-tame.
	Since $\HE_{\leq t}$ is constant with value $\HE$ for $t \geq 1$, the second assumption on the homology theory finishes the proof.
\end{proof}
